Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-09 paper/main.tex
Fixed typo
Added graphs and started on results table

\section{Results}

% Go graphs with plenty of short, descriptive comments.

@@

\parapgraph{Results are only valid for one specific computer}. The results we
used from \ac{SUPERCOP} are only valid for our specific computer, although it
gives an indication of which speeds can be achieved on similar computers, i.e.
32-bit. However to get a complete picture of the performance of the different
candidates one must look at different computers and architectures. This picture
might be obtained from looking at the results from all computeres measured by
\ac{SUPERCOP}.

>>>>

\section{Measurements of Tahoe operations}
%\vskip -1.5em % This is to fit in two graphs on one page including heading

The sum of the times it took for the underlying hash library to calculate the
hash operations are exhibited in Figures \ref{fig:graph:10001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{time spent hashing}.

The numbers for uploading and downloading of one 1GB file are summarized in
Tables \ref{tbl:hashingtimes:put1gb} and \ref{tbl:hashingtimes:get1gb}.

\input{tables/hashingtimes}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof10001Bfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof10001Bfiles.pdf}
    \caption{Figures for hash operations of 1000 1B files.}
    \label{fig:graph:10001b}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof1001KBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof1001KBfiles.pdf}
    \caption{Figures for hash operations of 100 1KB files.}
    \label{fig:graph:1001kb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof501MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof501MBfiles.pdf}
    \caption{Figures for hash operations of 50 1MB files.}
    \label{fig:graph:501mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof5100MBfiles.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof5100MBfiles.pdf}
    \caption{Figures for hash operations of five 100MB files.}
    \label{fig:graph:5100mb}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingPUTof11GBfile.pdf}
    \includegraphics[width=0.9\columnwidth]{graphs/TimespenthashingGETof11GBfile.pdf}
    \caption{Figures for hash operations of one 1GB file.}
    \label{fig:graph:11gb}
\end{figure}

@@

\paragraph{Results are only valid for one specific computer}. The results we
used from \ac{SUPERCOP} are only valid for our specific computer, although it
gives an indication of which speeds can be achieved on similar computers, i.e.
32-bit. However to get a complete picture of the performance of the different
candidates one must look at different computers and architectures. This picture
might be obtained from looking at the results from all computeres measured by
\ac{SUPERCOP}.
